### 2015-08-03 Irregular-occ/Irregular-occ.tex
Continuado artigo occ irregulares

We present in this paper the stellar occultation predictions for the 7 major irregular satellites of Jupiter (Himalia, Elara, Pasiphae, Lysithea, Carme, Ananke and Sinope), Phoebe from Saturn and Nereid from Neptune. In the section \ref{Sec: Rationale} we explore the scientific rationale for study the irregular satellites and the possibility of having a common origin with TNOs. In section \ref{Sec: Offset} we show the correction made to the ephemeris for better predict stellar occultations. In section \ref{Sec: predictions}, we present the predictions of the stellar occultations by irregular satellites and how they were made. Some test realized to confirm the predictions are presented in section \ref{Sec: testes} and the conclusion is given in section \ref{Sec: conclusions}.

@@

This idea is supported by the

@@

\begin{equation}
F(t,f) = p[0]\times \frac{t - jd_{0}}{365.65} + p[1]\times \sin(f) + p[2]\times\cos(f) + p[3],
\label{eq:linear}
\end{equation}

\begin{equation}
\begin{split}
%F = \{F_{x} \in  F_{c} &: (|S| > |C|) \\
% &\quad \cap (\text{minPixels}  < |S| < \text{maxPixels}) \\
% &\quad \cap (|S_{\text{conected}}| > |S| - \epsilon) \}
F(t,f) = p[0]\times\sin\left(\frac{2\pi}{p[1]}\times \frac{t - jd_{0}}{365.25} + p[2]\right) + p[3]\times\sin(f) + \\ +p[4]\times\cos(f) + p[5],
\end{split}
\end{equation}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in the section \ref{Sec: Offset}. The procedure to search for stellar candidates follows the same procedure presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}.

For Nereid, the candidates for stellar occultations in 2015 and 2016 was searched using the WFI catalogue in the same way as the predictions for Centaurs and TNOs occultations by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}. This catalogue contains the stars in the path of Neptune in the sky up to mid-2016. It was generated by observations made at the ESO 2p2 telescope (IAU code 809) using the Wide Field Imager (WFI) CCD mosaic detector. The filter used was the broad-band R filter ESO\#844 with $\lambda_c$ = 651.725 nm and $\Delta\lambda$ = 162.184 nm

@@

\begin{figure*}
\begin{centering}
\subfigure[Sem offsets]{\includegraphics[scale=0.19]{figures/Himalia1_2015-03-03T00:39:25.png}  \label{Fig: occ-Himalia-nooff}}
\subfigure[Offset de Himalia a partir do ajuste]{\includegraphics[scale=0.19]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[Obs. dia 22 de Fevereiro (campos separados)]{\includegraphics[scale=0.19]{figures/Himalia3_2015-03-03T00:39:40.png}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[Obs. dia 03 de Março (mesmo campo)]{\includegraphics[scale=0.19]{figures/Himalia4_2015-03-03T00:39:15.png}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: O ponto grande em vermelho mostra o ponto de máxima aproximação geocêntrica da sombra na Terra, os pontos vermelhos menores são os centros da ocultação separados por um minuto, as linhas retas são os limites das sombras dado o tamanho estimado do objeto e as linhas tracejadas equivalem a uma diferença de 40 mas do centro da sombra representando o erro estimado da predição. (a) é o mapa utilizando apenas as posições nominais da estrela e do satélite. (b) mostra a sombra dado um offset estimado para a posição de Himalia dada sua anomalia verdadeira segundo um ajuste feito em cima dos offsets de efeméride encontrados em \cite{GomesJunior2015-Irregular}. Em (c) são aplicados offsets às posições da estrela e do satélite a partir de observações feitas em 22 de Fevereiro no telescópio Zeiss. Em (d), temos o mesmo que para (c) porém com offsets obtidos de observações feitas em 03 de Março no telescópio Perkin-Elmer quando os objetos estavam próximos no campo.\textcolor{red}{Figuras e texto ainda serão mudados. Colocado para visualização}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

>>>>

We present in this paper the stellar occultation predictions for the 7 major irregular satellites of Jupiter (Himalia, Elara, Pasiphae, Lysithea, Carme, Ananke and Sinope), Phoebe from Saturn and Triton and Nereid from Neptune. In the section \ref{Sec: Rationale} we explore the scientific rationale for study the irregular satellites and the possibility of having a common origin with TNOs. In section \ref{Sec: Offset} we show the correction made to the ephemeris for better predict stellar occultations. In section \ref{Sec: predictions}, we present the predictions of the stellar occultations by irregular satellites and how they were made. Some test realized to confirm the predictions are presented in section \ref{Sec: testes} and the conclusion is given in section \ref{Sec: conclusions}.

@@

%This idea is supported by the

@@

\begin{equation}
F(t,f) = p[0]\times t + p[1]\times \sin(f) + p[2]\times\cos(f) + p[3],
\label{eq:linear}
\end{equation}

\begin{equation}
\begin{split}
%F = \{F_{x} \in  F_{c} &: (|S| > |C|) \\
% &\quad \cap (\text{minPixels}  < |S| < \text{maxPixels}) \\
% &\quad \cap (|S_{\text{conected}}| > |S| - \epsilon) \}
F(t,f) = p[0]\times\sin\left(\frac{2\pi}{p[1]}\times t + p[2]\right) + p[3]\times\sin(f) + \\ +p[4]\times\cos(f) + p[5],
\end{split}
\end{equation}
where $F(t,f)$ is the offset obtained, $t$ is time in years counting from J2000.0 and $f$ is the true anomaly.

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in the section \ref{Sec: Offset}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}.

It was predicted occultation by the 7 major irregular satellites of Jupiter, Phoebe of Saturn and Triton and Nereid of Neptune.

For Triton and Nereid, the candidates for stellar occultations in 2015 and 2016 was searched using the WFI catalogue in the same way as the predictions for Centaurs and TNOs occultations by \cite{Assafin2010, Assafin2012} and \cite{Camargo2013}. This catalogue contains the stars in the path of Neptune in the sky up to mid-2016. The catalogue was generated by observations made at the ESO 2p2 telescope (IAU code 809) using the Wide Field Imager (WFI) CCD mosaic detector. The filter used was the broad-band R filter ESO\#844 with $\lambda_c$ = 651.725 nm and $\Delta\lambda$ = 162.184 nm.

A total of 588 events \textcolor{red}{(Não estou contando ainda os eventos para Tritão)} were identified between January 2015 and December 2017. Table \ref{Tab: occ-list} exemplifies the catalogue of occultations generated and their parameters, which is necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table*}
\caption{\label{Tab: sample-cds} Extract of prediction table. \textcolor{red}{Ainda tenho que fazer a tabela melhor, encaixar. Abaixo é um exemplo apenas para visualização.}}
\begin{centering}
\begin{tabular}{ccccccccccccccccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
d m Year & h m s & \multicolumn{2}{c}{RA (ICRS) Dec} & C/A & P/A & v & D & R* & $\lambda$ & LST & $\Delta e_{\alpha *}$ & $\Delta e_{\delta}$ & pm & ct & $E_{\alpha *}$ & $E_{\delta}$ & $\mu_{\alpha *}$ & $\mu_{\delta}$ \tabularnewline
\hline
 07 10 2015 & 21 52 34. &  10 53 40.1835 & +08 21  00.489 & 0.465 & 200.31 & 39.31 & 6.25 & 16.6 & 179. & 09:48 & -31.0 & -13.0 & ok & uc &   0  &  0 & -13 &  -7 \tabularnewline
 23 10 2015 & 07 54 50. &  11 05 26.6037 & +07 14  32.030 & 1.017 & 201.33  & 36.11 & 6.12 & 15.5 & 16. & 08:59 & -31.0 & -13.0 & ok & uc &  0  &  0 &  -7 &  -4 \tabularnewline
%\texttt{ d  m year  h:m:s UT     ra\_\_\_dec\_\_\_J2000\_candidate     ra\_dec\_J2000\_target\_geocen     C/A    P/A     vel  Delta  R*   J*   H*   K*   long  loc. t.  off\_ra   off\_de pm ct f E\_ra E\_de pmra pmde} \tabularnewline
%\hline
% 05 01 2015  01 07  4.   09 32 20.9233 +15 35  10.584   09 32 20.9885 +15 35  12.220   1.888   29.94 -11.41  4.51 14.8 -0.6 -0.6 -0.6    22. 02:35     -31.0    -13.0 ok uc 0    0    0   -4    1 \tabularnewline
% 15 01 2015  01 03 15.   09 29  0.9265 +16 01  18.932   09 29  0.9610 +16 01  19.900   1.088   27.21 -13.17  4.45 14.8 -0.5 -0.5 -0.5    12. 01:52     -31.0    -13.0 ok uc 0    0    0   -2  -16 \tabularnewline
% 02 02 2015  08 03 30.   09 21 46.5321 +16 49  43.658   09 21 46.4857 +16 49  42.068   1.723  202.72 -14.32  4.40 16.0 -0.4 -0.4 -0.4   247. 00:32     -31.0    -13.0 ok uc 0    0    0    1   -8 \tabularnewline
% 14 02 2015  16 11 59.   09 16 41.4840 +17 18   2.448   09 16 41.4473 +17 18   0.976   1.563  199.68 -13.64  4.42 12.5 -0.4 -0.4 -0.4   112. 23:39     -31.0    -13.0 ok uc 0    0    0    5    0 \tabularnewline
% 25 02 2015  19 27 38.   09 12 25.6457 +17 38   6.563   09 12 25.6804 +17 38   8.217   1.727   16.72 -12.01  4.47 12.2 -0.6 -0.6 -0.6    51. 22:51     -31.0    -13.0 ok uc 0    0    0   -3    4 \tabularnewline
% 28 02 2015  09 17 38.   09 11 31.5455 +17 41  53.701   09 11 31.5720 +17 41  55.023   1.375   15.96 -11.50  4.49 14.1 -0.6 -0.6 -0.6   201. 22:40     -31.0    -13.0 ok uc 0    0    0  -16    6 \tabularnewline
% 03 03 2015  00 39 17.   09 10 38.6352 +17 45  26.467   09 10 38.6218 +17 45  25.758   0.734  195.15 -10.94  4.50 14.1 -0.7 -0.7 -0.7   327. 22:28     -31.0    -13.0 ok uc 0    0    0   -5    2 \tabularnewline
% 20 05 2015  08 59 41.   09 13 37.6521 +16 48  39.598   09 13 37.6915 +16 48  41.011   1.522   21.84  17.60  5.48 15.2 -0.1 -0.1 -0.1   126. 17:22     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 22 05 2015  06 52 27.   09 14 25.8437 +16 44   5.646   09 14 25.8400 +16 44   5.511   0.147  201.62  18.32  5.51 16.4 -0.1 -0.1 -0.1   156. 17:16     -31.0    -13.0 ok uc 0    0    0  -13    2 \tabularnewline
% 02 06 2015  16 14 18.   09 19 46.8676 +16 14  30.501   09 19 46.8693 +16 14  30.569   0.078   20.53  22.38  5.67 14.5  0.1  0.1  0.1     6. 16:36     -31.0    -13.0 ok uc 0    0    0   -7  -15 \tabularnewline
% 06 06 2015  02 41  6.   09 21 34.2809 +16 04  53.249   09 21 34.2951 +16 04  53.800   0.588   20.32  23.54  5.71 16.4  0.2  0.2  0.2   206. 16:24     -31.0    -13.0 ok uc 0    0    0    2    5 \tabularnewline
% 08 06 2015  20 25 31.   09 23  3.2029 +15 57   1.059   09 23  3.2057 +15 57   1.170   0.122   20.13  24.44  5.75 16.7  0.2  0.2  0.2   297. 16:15     -31.0    -13.0 ok uc 0    0    0   -3   -6 \tabularnewline
% 09 06 2015  22 29 56.   09 23 39.2777 +15 53  51.969   09 23 39.2451 +15 53  50.681   1.372  200.09  24.80  5.76 11.6  0.2  0.2  0.2   265. 16:11     -31.0    -13.0 ok uc 0    0    0    5  -24 \tabularnewline
% 20 06 2015  16 15 15.   09 29 57.6850 +15 21   0.007   09 29 57.7127 +15 21   1.135   1.198   19.56  28.11  5.90 16.4  0.4  0.4  0.4   350. 15:35     -31.0    -13.0 ok uc 0    0    0   -8   -1 \tabularnewline
% 05 07 2015  17 02 21.   09 39 45.6144 +14 31  18.362   09 39 45.6473 +14 31  19.747   1.465   19.04  32.07  6.06 16.7  0.5  0.5  0.5   326. 14:46     -31.0    -13.0 ok uc 0    0    0    0   -9 \tabularnewline
% 16 07 2015  03 15 38.   09 47  5.8941 +13 54  48.764   09 47  5.8853 +13 54  48.387   0.400  198.77  34.42  6.15 16.4  0.6  0.6  0.6   164. 14:12     -31.0    -13.0 ok uc 0    0    0  -19  -10 \tabularnewline
% 07 10 2015  21 52 34.   10 53 40.1835 +08 21   0.489   10 53 40.1726 +08 21   0.054   0.465  200.31  39.31  6.25 16.6  0.7  0.7  0.7   179. 09:48     -31.0    -13.0 ok uc 0    0    0  -13   -7 \tabularnewline
% 23 10 2015  07 54 50.   11 05 26.6037 +07 14  32.030   11 05 26.5789 +07 14  31.083   1.017  201.33  36.11  6.12 15.5  0.6  0.6  0.6    16. 08:59     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 31 10 2015  00 24 19.   11 10 56.2964 +06 42   7.110   11 10 56.3414 +06 42   8.782   1.801   21.84  33.94  6.04 16.9  0.6  0.6  0.6   123. 08:34     -31.0    -13.0 ok uc 0    0    0   -4  -13 \tabularnewline
% 07 11 2015  21 22 53.   11 16 14.3041 +06 10   5.194   11 16 14.2963 +06 10   4.912   0.306  202.36  31.33  5.94 16.2  0.5  0.5  0.5   162. 08:09     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 08 11 2015  04 27 21.   11 16 25.7881 +06 08  55.566   11 16 25.7606 +06 08  54.571   1.077  202.38  31.23  5.94 16.9  0.5  0.5  0.5    55. 08:08     -31.0    -13.0 ok uc 0    0    0    9  -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline

% 31 10 2015  00 24 19.   11 10 56.2964 +06 42   7.110   11 10 56.3414 +06 42   8.782   1.801   21.84  33.94  6.04 16.9  0.6  0.6  0.6   123. 08:34     -31.0    -13.0 ok uc 0    0    0   -4  -13 \tabularnewline
% 07 11 2015  21 22 53.   11 16 14.3041 +06 10   5.194   11 16 14.2963 +06 10   4.912   0.306  202.36  31.33  5.94 16.2  0.5  0.5  0.5   162. 08:09     -31.0    -13.0 ok uc 0    0    0    0    0 \tabularnewline
% 08 11 2015  04 27 21.   11 16 25.7881 +06 08  55.566   11 16 25.7606 +06 08  54.571   1.077  202.38  31.23  5.94 16.9  0.5  0.5  0.5    55. 08:08     -31.0    -13.0 ok uc 0    0    0    9  -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Occultation table: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates (corrected for the offset or ephemeris method), not presented here, of the occulting body; C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*, J*, H*, K*: normalized magnitudes to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$:offset in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); f = multiplicity flag (see Table 3); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

\begin{figure}
\begin{centering}
\includegraphics[scale=0.2]{figures/Himalia_2015-10-23T07:54:47.png} 
\caption{Occultation map for Himalia \textcolor{red}{Mapa de Himalia para exemplificar, posso colocar outro depois}. Compare the information given in caption with the second entry of Table \ref{Tab: occ-list}}
\label{Fig: ocultacao}
\end{centering}
\end{figure}

@@

Observe a stellar occultation by an irregular satellites demands a great effort. The shadow covers a very restricted area on Earth because the irregular satellites are small. So before we start a large observational campaign, we tested some occultation predictions for larger objects, to assess the quality of the prediction.

This test consists in observing the object and star to be occulted near the event when the two objects are present in the same field of view, preferably when the objects are close to each other. Thus the relative positions between the two objects will have minimal influence of the errors of the catalogue of stars used and possible field distortions.

To date, two occultation tests were performed, one by Himalia that occurred on March 3, 2015 and the second by Elara that occurred on March 30, 2015. For each event, four maps were generated: the first with the nominal positions of the star and the satellite to the predicted time; the second with the offset calculated as described in section \ref{Sec: Offset}; the third with star and satellite offsets from observations made a few days before the occultation when the two objects were separated (different FOV); and the fourth from observations made when the star and the satellite were close in the same FOV.

Figure \ref{Fig: occ-Himalia}. Shows the four maps for Himalia occultation test in March 03, 2015. The map \ref{Fig: occ-Himalia-nooff} is the nominal prediction with the coordinate of the star given by the catalogue and that of the satellite from the ephemeris. We then corrected the positions of the satellite by an offset calculated by the method showed in section \ref{Sec: Offset} to make the map \ref{Fig: occ-Himalia-ajuste}.

The map \ref{Fig: occ-Himalia-off22fev} was made from obtained positions on February 22 observed with the Zeiss telescope at the Observatório do Pico dos Dias (OPD). On that day, Himalia and the star were observed in separate FOVs as they were still far apart. On the night of the event, March 3, the objects were observed with Perkin-Elmer telescope at OPD just over an hour after the time scheduled for the event. Satellite and star were separated by about 16 arcsec, so very close to each other. From the calculated offsets, the map \ref{Fig: occ-Himalia-off03mar} was generated.

\begin{figure*}
\begin{centering}
\subfigure[Nominal prediction]{\includegraphics[scale=0.19]{figures/Himalia1_2015-03-03T00:39:25.png}  \label{Fig: occ-Himalia-nooff}}
\subfigure[\textcolor{red}{Offset de Himalia a partir do ajuste}]{\includegraphics[scale=0.19]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[February 22 observations (different FOVs)]{\includegraphics[scale=0.19]{figures/Himalia3_2015-03-03T00:39:40.png}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[March 03 observation (same FOV)]{\includegraphics[scale=0.19]{figures/Himalia4_2015-03-03T00:39:15.png}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The big red dot show the geocentric closest approach of the shadow. The small red ones are the center of the shadow separated by one minute. The straight lines show the size of the shadow. \ref{Fig: occ-Himalia-nooff} is the map using the nominal positions of the star and satellite. \ref{Fig: occ-Himalia-ajuste} shows the shadow given an estimated offset for the position of Himalia related to the JPL ephemeris obtained in section \ref{Sec: Offset}. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. In \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. \textcolor{red}{Figuras ainda serão mudadas. Colocadas para visualização}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

In this event, it is possible to see that the shade does not vary much among the four maps suggesting that, at least for Himalia, there is a greater probability of observing an event. In fact, the biggest difference between the shadows of the four maps are 25s and 130km in the direction perpendicular to the shadows (see table \ref{Tab: comparison-Himalia}).

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of Himalia. \textcolor{red}{Ainda vou terminar de preencher a tabela e tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
Nominal & 2015-03-03 00:39:25 UT & $0.714\arcsec$ \tabularnewline
Offset & -07 s & \tabularnewline
Feb. 22 Obs. & +15 s &  \tabularnewline
Mar. 03 Obs. & -10 s & \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}

The second test was with the satellite Elara, which is the second biggest irregular satellites of Jupiter. The event was predict the occur at March 30, 2015. The observations were taken on March 25 and April 2, 2015 with the Zeiss telescope. On the night of April 2 they could still be observed in the same FOV. Due to Elara be much weaker, dispersions of the satellite positions on both nights ended up being higher than for Himalia. Still, the differences between the maps obtained were relatively small. The biggest difference between them is 73s and 302km (see table \ref{Tab: comparison-Elara}).

\begin{table}
\caption{\label{Tab: comparison-Elara} Comparison between the predictions of Elara. \textcolor{red}{Ainda vou terminar de preencher a tabela e tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A  \tabularnewline
\hline
Nominal & 2015-03-30 01:45:15 UT & $1.139\arcsec$ \tabularnewline
Offset & -16 s & \tabularnewline
Mar. 25 Obs. & -58 s &  \tabularnewline
Apr. 02 Obs. & +15 s & \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}
